---
title: "Data_Cleanup"
author: "Sara Knight"
date: "7/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading_library}

library(tidyverse)
library(tidymodels)
library(stringr)

```


```{r loading_data}

books<- read_csv("~/STA_631/Projects/book_ban_project/data/Book_Challenge_Data.csv")
books2<- read_csv("~/STA_631/Projects/book_ban_project/data/df_books.csv")

```

Got rid of all of the books that had no Goodreads tags.

```{r droping_NAs}

books <- books %>% drop_na(Book_Tag)

```


Cleaned up the string of booktags
```{r cleaned_book_tag_column}

books$Book_Tag <- str_to_title(books$Book_Tag)

```

Got rid of all the white space between the words to help fix some of the human errors
```{r getting_rid_of_whitespace}

books$Book_Tag <-gsub(" ", "", books$Book_Tag, fixed = TRUE)

```



Separated the book tags for the challenged books into their own individual columns.
```{r separating_book_tag}

book_tag <-books %>% 
   separate(Book_Tag,c("Book_Tag1","Book_Tag2", "Book_Tag3", "Book_Tag4",
                       "Book_Tag5", "Book_Tag6", "Book_Tag7",
                       "Book_Tag8","Book_Tag9"),sep=",")

```


I made a data set of just tags so that I could see how frequently the tags showed up
```{r maknig_a_data_frame_with_just_tags}
tags <- book_tag[,c(3:11)]
```

```{r counting_tag_occurences}
count <- table(unlist(tags))
```

```{r making_it_into_a_dataframe}
count <- as.data.frame(count)
```

```{r ordering_count}
count <- count[order(count$Freq, decreasing=TRUE),]
```

Did the same for the other book tag
```{r fixinging_book_tag2}

books2$Book_Tag <- str_to_title(books2$Book_Tag)

```

```{r getting_rid_of_whitespace2}

books2$Book_Tag <-gsub(" ", "", books2$Book_Tag, fixed = TRUE)

```

```{r separating_into_individual_booktags2}

books2 <-books2  %>% 
   separate(Book_Tag,c("Book_Tag1","Book_Tag2", "Book_Tag3", "Book_Tag4",
                       "Book_Tag5", "Book_Tag6", "Book_Tag7",
                       "Book_Tag8","Book_Tag9"),sep=",")

```

To simplify the project I decided to look at only ya books. The reasoning behind this is that these book challenges are there to "protect the children", and that is why I didn't pick adult. At the same time if I chose young adult, there would be chance that I could get some spill over into the other two categories.
```{r finding_young_adult_book}

ya_books <- books %>% filter(grepl('YoungAdult', Book_Tag))

```


```{r separating_ya_book_tags}

ya_tags <- ya_books  %>% 
   separate(Book_Tag,c("Book_Tag1","Book_Tag2", "Book_Tag3", "Book_Tag4",
                       "Book_Tag5", "Book_Tag6", "Book_Tag7",
                       "Book_Tag8","Book_Tag9"),sep=",")


```
Creating a dataframe to look at the counts on individual tags in the the challenged ya books
```{r ya_tag_dataframe}
ya_count <- ya_tags[,c(3:11)]
```

```{r counting_individual_tags2}
ya_count <- table(unlist(ya_count))
```

```{r turning_it_into_a_data_frame2}
ya_count <- as.data.frame(ya_count)
```

```{r ordering_the_dataframe}
ya_count <- ya_count[order(ya_count$Freq, decreasing=TRUE),]
```


Due to time constraints I was only able to find 386 young adult books that weren't challenged to build the model, so I had to take a sample of the challenged ya books.
```{r grabing_a_collection_of_ya_books}
set.seed(123)

ya_sample <- ya_books[sample(1:nrow(ya_books), 386), ]
```

breaking the challenged ya books tags into individual columns
```{r finding_sample_books_tag}

ya_sample <-ya_sample  %>% 
   separate(Book_Tag,c("Book_Tag1","Book_Tag2", "Book_Tag3", "Book_Tag4",
                       "Book_Tag5", "Book_Tag6", "Book_Tag7",
                       "Book_Tag8","Book_Tag9"),sep=",")

```
```{r reodrering_columns_so_I_can_bind_together}
ya_sample <- ya_sample[,c(2,1,3:12)]
```

```{r renaming_column_names}

colnames(books2)[1] = "Book_Title"

```

```{r renaming_column_names2}

colnames(ya_sample)[12] = "Challenged"

```

```{r binding_two_dataframes_together}
book_data <- rbind(ya_sample, books2)
```

Here I created a copy of the data for a later idea.
```{r creating_a_copy_of_the_data}
book_domain <- book_data
```

```{r randomizing_the_order_of_the_data}
book_data <- book_data[sample(1:nrow(book_data)), ]
```

My first idea is to look that top tags in the challenged ya books data set and see if that tells me anything. The first two tags are YoungAdult and Fiction. YoungAdult should be tagged in every book and ultimately won't be helpful. With Fiction I think this will be tagged on a lot of books. Also there will be more specific fiction tags like RealisticFiction and HistoricalFiction.
I chose to look at how the top five tags for the challenged data would look like.

```{r making_a_dummy_for_Contemporary}

book_data <- book_data %>%
  mutate(Contemporary = case_when(Book_Tag1 == 'Contemporary' | 
                          Book_Tag2 == 'Contemporary' | 
                          Book_Tag3 == 'Contemporary' | 
                          Book_Tag4 == 'Contemporary' | 
                          Book_Tag5 == 'Contemporary' | 
                          Book_Tag6 == 'Contemporary' | 
                          Book_Tag7 == 'Contemporary' | 
                          Book_Tag8 == 'Contemporary' |
                          Book_Tag9 == 'Contemporary'~1,
                           TRUE ~ 0))
```

```{r making_a_dummy_for_Romance}

book_data <- book_data %>%
  mutate(Romance = case_when(Book_Tag1 == 'Romance' | 
                             Book_Tag2 == 'Romance' | 
                             Book_Tag3 == 'Romance' | 
                             Book_Tag4 == 'Romance' | 
                             Book_Tag5 == 'Romance' | 
                             Book_Tag6 == 'Romance' | 
                             Book_Tag7 == 'Romance' | 
                             Book_Tag8 == 'Romance' |
                             Book_Tag9 == 'Romance'~1,
                           TRUE ~ 0))
```

```{r making_a_dummy_for_LGBT}

book_data <- book_data %>%
  mutate(LGBT = case_when(Book_Tag1 == 'Lgbt' | 
                          Book_Tag2 == "Lgbt" | 
                          Book_Tag3 == 'Lgbt' | 
                          Book_Tag4 == "Lgbt" | 
                          Book_Tag5 == 'Lgbt' | 
                          Book_Tag6 == "Lgbt" | 
                          Book_Tag7 == 'Lgbt' | 
                          Book_Tag8 == "Lgbt" |
                          Book_Tag9 == "Lgbt"~1,
                          TRUE ~ 0))
```

```{r making_a_dummy_for_Realistic_Fiction}

book_data <- book_data %>%
  mutate(Realistic_Fiction = case_when(Book_Tag1 == 'RealisticFiction' | 
                                       Book_Tag2 == 'RealisticFiction' | 
                                       Book_Tag3 == 'RealisticFiction' | 
                                       Book_Tag4 == 'RealisticFiction' | 
                                       Book_Tag5 == 'RealisticFiction' | 
                                       Book_Tag6 == 'RealisticFiction' | 
                                       Book_Tag7 == 'RealisticFiction' | 
                                       Book_Tag8 == 'RealisticFiction' |
                                       Book_Tag9 == 'RealisticFiction'~1,
                                       TRUE ~ 0))
```

I skipped the queer tag because if a book was tagged with a subset of the LGBT community it was also tagged with LGBT.

```{r making_a_dummy_for_Fantasy}

book_data <- book_data %>%
  mutate(Fantasy = case_when(Book_Tag1 == 'Fantasy' | 
                             Book_Tag2 == 'Fantasy' | 
                             Book_Tag3 == 'Fantasy' | 
                             Book_Tag4 == 'Fantasy' | 
                             Book_Tag5 == 'Fantasy' | 
                             Book_Tag6 == 'Fantasy' | 
                             Book_Tag7 == 'Fantasy' | 
                             Book_Tag8 == 'Fantasy' |
                             Book_Tag9 == 'Fantasy'~1,
                                       TRUE ~ 0))
```

I excluded teen because that was another way of saying Young Adult.

```{r making_a_dummy_for_Middle_Grade}

book_data <- book_data %>%
  mutate(Middle_Grade = case_when(Book_Tag1 == 'MiddleGrade' | 
                                  Book_Tag2 == 'MiddleGrade' | 
                                  Book_Tag3 == 'MiddleGrade' | 
                                  Book_Tag4 == 'MiddleGrade' | 
                                  Book_Tag5 == 'MiddleGrade' | 
                                  Book_Tag6 == 'MiddleGrade' | 
                                  Book_Tag7 == 'MiddleGrade' | 
                                  Book_Tag8 == 'MiddleGrade' |
                                  Book_Tag9 == 'MiddleGrade'~1,
                                    TRUE ~ 0))
```

I also didn't include Audiobook because that says more about how people are consuming books rather than the contents of the book

```{r making_a_dummy_for_Historical_Fiction}

book_data <- book_data %>%
  mutate(Historical_Fiction = case_when(Book_Tag1 == 'HistoricalFiction' | 
                                        Book_Tag2 == 'HistoricalFiction' | 
                                        Book_Tag3 == 'HistoricalFiction' | 
                                        Book_Tag4 == 'HistoricalFiction' | 
                                        Book_Tag5 == 'HistoricalFiction' | 
                                        Book_Tag6 == 'HistoricalFiction' | 
                                        Book_Tag7 == 'HistoricalFiction' | 
                                        Book_Tag8 == 'HistoricalFiction' |
                                        Book_Tag9 == 'HistoricalFiction'~1,
                                    TRUE ~ 0))
```

```{r making_a_dummy_for_Graphic_Novels}

book_data <- book_data %>%
  mutate(Graphic_Novels = case_when(Book_Tag1 == 'GraphicNovels' | 
                                    Book_Tag2 == 'GraphicNovels' | 
                                    Book_Tag3 == 'GraphicNovels' | 
                                    Book_Tag4 == 'GraphicNovels' | 
                                    Book_Tag5 == 'GraphicNovels' | 
                                    Book_Tag6 == 'GraphicNovels' | 
                                    Book_Tag7 == 'GraphicNovels' | 
                                    Book_Tag8 == 'GraphicNovels' |
                                    Book_Tag9 == 'GraphicNovels'~1,
                                    TRUE ~ 0))
```

I didn't include Comics for the same reason I didn't include Queer Books.

```{r making_a_dummy_for_Mystery}

book_data <- book_data %>%
  mutate(Mystery = case_when(Book_Tag1 == 'Mystery' | 
                             Book_Tag2 == 'Mystery' | 
                             Book_Tag3 == 'Mystery' | 
                             Book_Tag4 == 'Mystery' | 
                             Book_Tag5 == 'Mystery' | 
                             Book_Tag6 == 'Mystery' | 
                             Book_Tag7 == 'Mystery' | 
                             Book_Tag8 == 'Mystery' |
                             Book_Tag9 == 'Mystery'~1,
                                       TRUE ~ 0))
```

```{r splitting_the_data}

set.seed(123)

books_split <- initial_split(book_data, 0.8)

book_train <- training(books_split)

book_test <- testing(books_split)

```

```{r logistical_regression}

log_reg <- glm(Challenged ~ LGBT + Contemporary + Romance + Realistic_Fiction + Fantasy + Middle_Grade + Graphic_Novels + Historical_Fiction + Mystery
               , data = book_train, family = "binomial")

summary(log_reg)
```

```{r logistic_regression2}

log_reg2 <- glm(Challenged ~ LGBT + Realistic_Fiction + Middle_Grade + Graphic_Novels, data = book_train, family = "binomial")

summary(log_reg2)
```

The formula for the logistic regression is:
$$

\begin{aligned}
\hat{Challenged} = -1.0713 +  5.1379 \times LGBT + 1.9035 \times Realistic Fiction\\ 
+ -1.2450  \times Middle Grade + 3.0714 Grapic Novels
\end{aligned}

$$

``` {r}
  tidy(log_reg2, exponentiate = TRUE) %>% 
    knitr::kable(digits = 3)
```

``` {r predicted_vs_residuals}
# To store residuals and create row number variable
log_aug <- augment(log_reg2, type.predict = "response", 
                   type.residuals = "deviance") %>% 
  mutate(id = row_number())

# Plot residuals vs fitted values
ggplot(data = log_aug, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "Fitted values", 
       y = "Deviance residuals", 
       title = "Deviance residuals vs. fitted")

# Plot residuals vs row number
ggplot(data = log_aug, aes(x = id, y = .resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "id", 
       y = "Deviance residuals", 
       title = "Deviance residuals vs. id")
```
The graphs show there are no extreme outliers when it comes to the residuals. So overall I don't think this is a bad fit.


```{r finding_r_squared}
require(rms)
finding_r_squared <- lrm(Challenged ~ LGBT + Realistic_Fiction + Middle_Grade + Graphic_Novels, data = book_test)

finding_r_squared
```
I found this [stackExchange] (https://stats.stackexchange.com/questions/8511/how-to-calculate-pseudo-r2-from-rs-logistic-regression#:~:text=Technically%2C%20R2%20cannot%20be,model%20with%20constant%20and%20predictors.) website to look at how to find the psuedo-R^2 from a logistic regression. I don't know how appropriate an R^2 is in this occasion, but I wanted to find it to give myself some context. In this case it 62.4 which is a lot higher than I though it was going to be.

Looking again at the equation:
$$

\begin{aligned}
\hat{Challenged} = -1.0713 +  5.1379 \times LGBT + 1.9035 \times Realistic Fiction\\ 
+ -1.2450  \times Middle Grade + 3.0714 Grapic Novels
\end{aligned}

$$

```{r interpreting_LGBT_coefficient}

exp(5.1279)

```
This means keeping everything the same books with an LGBT are 168.66 times likely to get challenged.

```{r interpreting_Realistic_Fiction_coefficient}
exp(1.9035)
```
Again keeping everything the same books with Realistic Fiction ate 6.71 times likely to get challenged

```{r interpreting_Middle_Grade_coefficient}
exp(-1.2450)
```
Keeping everything the same books with a Middle Grade tage are 0.29 times likely to get challenged

```{r interpreting_Graphic_Novel_coefficient}
exp(3.0714)
```
Finally, again keeping everything the same a book with a Graphic Novel tag is 21.57 times likely to get challenged.

My next idea is to try using the domain expertise I have, following the story in the media, and putting myself into the perspective of a parent looking to ban books. This mainly for fun and to see what I come up with.

So, I went through the tags and tried to find the tags that would be featured in challenged books. These are things like LGBT, Mental Health, New Adult, and so on.

```{r making_an_LGBT_dummy_variable}

book_domain <- book_domain %>%
  mutate(LGBT= case_when(Book_Tag1 == 'Lgbt' | 
                         Book_Tag2 == 'Lgbt' | 
                         Book_Tag3 == 'Lgbt' | 
                         Book_Tag4 == 'Lgbt' | 
                         Book_Tag5 == 'Lgbt' | 
                         Book_Tag6 == 'Lgbt' | 
                         Book_Tag7 == 'Lgbt' | 
                         Book_Tag8 == 'Lgbt' |
                         Book_Tag9 == 'Lgbt'~1,
                                    TRUE ~ 0))
```

```{r making_a_Mental_Health_dummy_variable}

book_domain <- book_domain %>%
  mutate(Mental_Health = case_when(Book_Tag1 == 'MentalHealth' | 
                                   Book_Tag2 == 'MentalHealth' | 
                                   Book_Tag3 == 'MentalHealth' | 
                                   Book_Tag4 == 'MentalHealth' | 
                                   Book_Tag5 == 'MentalHealth' | 
                                   Book_Tag6 == 'MentalHealth' | 
                                   Book_Tag7 == 'MentalHealth' | 
                                   Book_Tag8 == 'MentalHealth' |
                                   Book_Tag9 == 'MentalHealth'~1,
                                   TRUE ~ 0))
```

```{r making_a_New_Adult_dummy_variable}

book_domain <- book_domain %>%
  mutate(New_Adult = case_when(Book_Tag1 == 'NewAdult' | 
                               Book_Tag2 == 'NewAdult' | 
                               Book_Tag3 == 'NewAdult' | 
                               Book_Tag4 == 'NewAdult' |                                                                   Book_Tag5 == 'NewAdult' | 
                               Book_Tag6 == 'NewAdult' | 
                               Book_Tag7 == 'NewAdult' |                                                                   Book_Tag8 == 'NewAdult' |
                               Book_Tag9 == 'NewAdult'~1,
                              TRUE ~ 0))
```

```{r making_a_Thriller_dummy_variable}

book_domain <- book_domain %>%
  mutate(Thriller = case_when(Book_Tag1 == 'Thriller' | 
                              Book_Tag2 == 'Thriller' | 
                              Book_Tag3 == 'Thriller' | 
                              Book_Tag4 == 'Thriller' |                                                                   Book_Tag5 == 'Thriller' | 
                              Book_Tag6 == 'Thriller' | 
                              Book_Tag7 == 'Thriller' |                                                                   Book_Tag8 == 'Thriller' |
                              Book_Tag9 == 'Thriller'~1,
                              TRUE ~ 0))
```

```{r making_a_Dystopia_dummy_variable}

book_domain <- book_domain %>%
  mutate(Dystopia = case_when(Book_Tag1 == 'Dystopia' | 
                              Book_Tag2 == 'Dystopia' | 
                              Book_Tag3 == 'Dystopia' | 
                              Book_Tag4 == 'Dystopia' |                                                                   Book_Tag5 == 'Dystopia' | 
                              Book_Tag6 == 'Dystopia' | 
                              Book_Tag7 == 'Dystopia' |                                                                   Book_Tag8 == 'Dystopia' |
                              Book_Tag9 == 'Dystopia'~1,
                              TRUE ~ 0))
```

```{r making_an_Abuse_dummy_variable}

book_domain <- book_domain %>%
  mutate(Abuse = case_when(Book_Tag1 == 'Abuse' | 
                           Book_Tag2 == 'Abuse' | 
                           Book_Tag3 == 'Abuse' | 
                           Book_Tag4 == 'Abuse' |                                                                      Book_Tag5 == 'Abuse' | 
                           Book_Tag6 == 'Abuse' | 
                           Book_Tag7 == 'Abuse' |                                                                      Book_Tag8 == 'Abuse' |
                           Book_Tag9 == 'Abuse'~1,
                              TRUE ~ 0))
```

```{r making_a_Horror_dummy_variable}

book_domain <- book_domain %>%
  mutate(Horror = case_when(Book_Tag1 == 'Horror' | 
                            Book_Tag2 == 'Horror' | 
                            Book_Tag3 == 'Horror' | 
                            Book_Tag4 == 'Horror' |                                                                     Book_Tag5 == 'Horror' | 
                            Book_Tag6 == 'Horror' | 
                            Book_Tag7 == 'Horror' |                                                                     Book_Tag8 == 'Horror' |
                            Book_Tag9 == 'Horror'~1,
                              TRUE ~ 0))
```

```{r making_a_Manga_dummy_variable}

book_domain <- book_domain %>%
  mutate(Manga = case_when(Book_Tag1 == 'Manga' | 
                           Book_Tag2 == 'Manga' | 
                           Book_Tag3 == 'Manga' | 
                           Book_Tag4 == 'Manga' |                                                                      Book_Tag5 == 'Manga' | 
                           Book_Tag6 == 'Manga' | 
                           Book_Tag7 == 'Manga' |                                                                      Book_Tag8 == 'Manga' |
                           Book_Tag9 == 'Manga'~1,
                              TRUE ~ 0))
```

```{r making_an_African_American_dummy_variable}

book_domain <- book_domain %>%
  mutate(African_American = case_when(Book_Tag1 == 'AfricanAmerican' | 
                                      Book_Tag2 == 'AfricanAmerican' | 
                                      Book_Tag3 == 'AfricanAmerican' |
                                      Book_Tag4 == 'AfricanAmerican' | 
                                      Book_Tag5 == 'AfricanAmerican' |
                                      Book_Tag6 == 'AfricanAmerican' | 
                                      Book_Tag7 == 'AfricanAmerican' |                      
                                      Book_Tag8 == 'AfricanAmerican' |
                                      Book_Tag9 == 'AfricanAmerican'~1,
                                      TRUE ~ 0))
```

```{r making_a_Mental_Illness_dummy_variable}

book_domain <- book_domain %>%
  mutate(Mental_Illness = case_when(Book_Tag1 == 'MentalIllness' | 
                                    Book_Tag2 == 'MentalIllness' | 
                                    Book_Tag3 == 'MentalIllness' |
                                    Book_Tag4 == 'MentalIllness' | 
                                    Book_Tag5 == 'MentalIllness' |
                                    Book_Tag6 == 'MentalIllness' | 
                                    Book_Tag7 == 'MentalIllness' |                      
                                    Book_Tag8 == 'MentalIllness' |
                                    Book_Tag9 == 'MentalIllness'~1,
                                    TRUE ~ 0))
```

```{r making_a_Social_Justice_dummy_variable}

book_domain <- book_domain %>%
  mutate(Social_Justice = case_when(Book_Tag1 == 'SocialJustice' | 
                                    Book_Tag2 == 'SocialJustice' | 
                                    Book_Tag3 == 'SocialJustice' |
                                    Book_Tag4 == 'SocialJustice' | 
                                    Book_Tag5 == 'SocialJustice' |
                                    Book_Tag6 == 'SocialJustice' | 
                                    Book_Tag7 == 'SocialJustice' |                      
                                    Book_Tag8 == 'SocialJustice' |
                                    Book_Tag9 == 'SocialJustice'~1,
                                    TRUE ~ 0))
```

```{r making_a_Witches_dummy_variable}

book_domain <- book_domain %>%
  mutate(Witches = case_when(Book_Tag1 == 'Witches' | 
                             Book_Tag2 == 'Witches' | 
                             Book_Tag3 == 'Witches' |
                             Book_Tag4 == 'Witches' | 
                             Book_Tag5 == 'Witches' |
                             Book_Tag6 == 'Witches' | 
                             Book_Tag7 == 'Witches' |                      
                             Book_Tag8 == 'Witches' |
                             Book_Tag9 == 'Witches'~1,
                             TRUE ~ 0))
```

```{r making_a_Race_dummy_variable}

book_domain <- book_domain %>%
  mutate( Race = case_when(Book_Tag1 == 'Race' | 
                           Book_Tag2 == 'Race' | 
                           Book_Tag3 == 'Race' |
                           Book_Tag4 == 'Race' | 
                           Book_Tag5 == 'Race' |
                           Book_Tag6 == 'Race' | 
                           Book_Tag7 == 'Race' |                      
                           Book_Tag8 == 'Race' |
                           Book_Tag9 == 'Race'~1,
                           TRUE ~ 0))
```

```{r making_a_War_dummy_variable}

book_domain <- book_domain %>%
  mutate( War = case_when(Book_Tag1 == 'War' | 
                          Book_Tag2 == 'War' | 
                          Book_Tag3 == 'War' |
                          Book_Tag4 == 'War' | 
                          Book_Tag5 == 'War' |
                          Book_Tag6 == 'War' | 
                          Book_Tag7 == 'War' |                      
                          Book_Tag8 == 'War' |
                          Book_Tag9 == 'War'~1,
                          TRUE ~ 0))
```

```{r making_a_Crime_dummy_variable}

book_domain <- book_domain %>%
  mutate( Crime = case_when(Book_Tag1 == 'Crime' | 
                            Book_Tag2 == 'Crime' | 
                            Book_Tag3 == 'Crime' |
                            Book_Tag4 == 'Crime' | 
                            Book_Tag5 == 'Crime' |
                            Book_Tag6 == 'Crime' | 
                            Book_Tag7 == 'Crime' |                      
                            Book_Tag8 == 'Crime' |
                            Book_Tag9 == 'Crime'~1,
                            TRUE ~ 0))
```

```{r making_a_Death_dummy_variable}

book_domain <- book_domain %>%
  mutate( Death = case_when(Book_Tag1 == 'Death' | 
                            Book_Tag2 == 'Death' | 
                            Book_Tag3 == 'Death' |
                            Book_Tag4 == 'Death' | 
                            Book_Tag5 == 'Death' |
                            Book_Tag6 == 'Death' | 
                            Book_Tag7 == 'Death' |                      
                            Book_Tag8 == 'Death' |
                            Book_Tag9 == 'Death'~1,
                            TRUE ~ 0))
```

```{r making_a_Religion_dummy_variable}

book_domain <- book_domain %>%
  mutate( Religion = case_when(Book_Tag1 == 'Religion' | 
                               Book_Tag2 == 'Religion' | 
                               Book_Tag3 == 'Religion' |
                               Book_Tag4 == 'Religion' | 
                               Book_Tag5 == 'Religion' |
                               Book_Tag6 == 'Religion' | 
                               Book_Tag7 == 'Religion' |                      
                               Book_Tag8 == 'Religion' |
                               Book_Tag9 == 'Religion'~1,
                               TRUE ~ 0))
```

```{r making_a_Politics_dummy_variable}

book_domain <- book_domain %>%
  mutate( Politics = case_when(Book_Tag1 == 'Politics' | 
                               Book_Tag2 == 'Politics' | 
                               Book_Tag3 == 'Politics' |
                               Book_Tag4 == 'Politics' | 
                               Book_Tag5 == 'Politics' |
                               Book_Tag6 == 'Politics' | 
                               Book_Tag7 == 'Politics' |                      
                               Book_Tag8 == 'Politics' |
                               Book_Tag9 == 'Politics'~1,
                               TRUE ~ 0))
```

```{r making_a_Sexuality_dummy_variable}

book_domain <- book_domain %>%
  mutate( Sexuality = case_when(Book_Tag1 == 'Sexuality' | 
                                Book_Tag2 == 'Sexuality' | 
                                Book_Tag3 == 'Sexuality' |
                                Book_Tag4 == 'Sexuality' | 
                                Book_Tag5 == 'Sexuality' |
                                Book_Tag6 == 'Sexuality' | 
                                Book_Tag7 == 'Sexuality' |                      
                                Book_Tag8 == 'Sexuality' |
                                Book_Tag9 == 'Sexuality'~1,
                                TRUE ~ 0))
``` 

```{r making_an_Africa_dummy_variable}

book_domain <- book_domain %>%
  mutate( Africa = case_when(Book_Tag1 == 'Africa' | 
                             Book_Tag2 == 'Africa' | 
                             Book_Tag3 == 'Africa' |
                             Book_Tag4 == 'Africa' | 
                             Book_Tag5 == 'Africa' |
                             Book_Tag6 == 'Africa' |   
                             Book_Tag7 == 'Africa' |                      
                             Book_Tag8 == 'Africa' |
                             Book_Tag9 == 'Africa'~1,
                            TRUE ~ 0))
``` 

```{r making_an_Autism_dummy_variable}

book_domain <- book_domain %>%
  mutate( Autism = case_when(Book_Tag1 == 'AutismSpectrumDisorder' | 
                             Book_Tag2 == 'AutismSpectrumDisorder' | 
                             Book_Tag3 == 'AutismSpectrumDisorder' |
                             Book_Tag4 == 'AutismSpectrumDisorder' | 
                             Book_Tag5 == 'AutismSpectrumDisorder' |
                             Book_Tag6 == 'AutismSpectrumDisorder' |
                             Book_Tag7 == 'AutismSpectrumDisorder' |                      
                             Book_Tag8 == 'AutismSpectrumDisorder' |
                             Book_Tag9 == 'AutismSpectrumDisorder'~1,
                             TRUE ~ 0))
``` 

```{r making_a_Cult_dummy_variable}

book_domain <- book_domain %>%
  mutate( Cults = case_when(Book_Tag1 == 'Cults' | 
                            Book_Tag2 == 'Cults' | 
                            Book_Tag3 == 'Cults' |
                            Book_Tag4 == 'Cults' | 
                            Book_Tag5 == 'Cults' |
                            Book_Tag6 == 'Cults' |
                            Book_Tag7 == 'Cults' |                      
                            Book_Tag8 == 'Cults' |
                            Book_Tag9 == 'Cults'~1,
                            TRUE ~ 0))
``` 

```{r making_a_Dark_dummy_variable}

book_domain <- book_domain %>%
  mutate( Dark = case_when(Book_Tag1 == 'Dark' | 
                           Book_Tag2 == 'Dark' | 
                           Book_Tag3 == 'Dark' |
                           Book_Tag4 == 'Dark' | 
                           Book_Tag5 == 'Dark' |
                           Book_Tag6 == 'Dark' |
                           Book_Tag7 == 'Dark' |                      
                           Book_Tag8 == 'Dark' |
                           Book_Tag9 == 'Dark'~1,
                          TRUE ~ 0))
``` 

```{r making_a_Disablity_dummy_variable}

book_domain <- book_domain %>%
  mutate( Disability = case_when(Book_Tag1 == 'Disability' | 
                                 Book_Tag2 == 'Disability' | 
                                 Book_Tag3 == 'Disability' |
                                 Book_Tag4 == 'Disability' | 
                                 Book_Tag5 == 'Disability' |
                                 Book_Tag6 == 'Disability' |
                                 Book_Tag7 == 'Disability' |                      
                                 Book_Tag8 == 'Disability' |
                                 Book_Tag9 == 'Disability'~1,
                                TRUE ~ 0))
``` 

```{r making_a_Jewish_dummy_variable}

book_domain <- book_domain %>%
  mutate( Jewish = case_when(Book_Tag1 == 'Jewish' | 
                             Book_Tag2 == 'Jewish' | 
                             Book_Tag3 == 'Jewish' |
                             Book_Tag4 == 'Jewish' | 
                             Book_Tag5 == 'Jewish' |
                             Book_Tag6 == 'Jewish' |
                             Book_Tag7 == 'Jewish' |                      
                             Book_Tag8 == 'Jewish' |
                             Book_Tag9 == 'Jewish'~1,
                             TRUE ~ 0))
``` 

```{r making_a_Science_dummy_variable}

book_domain <- book_domain %>%
  mutate(  Science = case_when(Book_Tag1 == 'Science' | 
                               Book_Tag2 == 'Science' | 
                               Book_Tag3 == 'Science' |
                               Book_Tag4 == 'Science' | 
                               Book_Tag5 == 'Science' |
                               Book_Tag6 == 'Science' |
                               Book_Tag7 == 'Science' |                      
                               Book_Tag8 == 'Science' |
                               Book_Tag9 == 'Science'~1,
                              TRUE ~ 0))
``` 

```{r making_a_Senin_dummy_variable}

book_domain <- book_domain %>%
  mutate( Seinen = case_when(Book_Tag1 == 'Seinen' | 
                             Book_Tag2 == 'Seinen' | 
                             Book_Tag3 == 'Seinen' |
                             Book_Tag4 == 'Seinen' | 
                             Book_Tag5 == 'Seinen' |
                             Book_Tag6 == 'Seinen' |
                             Book_Tag7 == 'Seinen' |
                             Book_Tag8 == 'Seinen' |
                             Book_Tag9 == 'Seinen'~1,
                             TRUE ~ 0))
``` 

```{r making_a_Women_dummy_variable}

book_domain <- book_domain %>%
  mutate( Womens = case_when(Book_Tag1 == 'Womens' | 
                             Book_Tag2 == 'Womens' | 
                             Book_Tag3 == 'Womens' |
                             Book_Tag4 == 'Womens' | 
                             Book_Tag5 == 'Womens' |
                             Book_Tag6 == 'Womens' |
                             Book_Tag7 == 'Womens' |                      
                             Book_Tag8 == 'Womens' |
                             Book_Tag9 == 'Womens'~1,
                            TRUE ~ 0))
``` 

```{r making_a_Shojo_dummy_variable}

book_domain <- book_domain %>%
  mutate( Shojo = case_when(Book_Tag1 == 'Shojo' | 
                            Book_Tag2 == 'Shojo' | 
                            Book_Tag3 == 'Shojo' |
                            Book_Tag4 == 'Shojo' | 
                            Book_Tag5 == 'Shojo' |
                            Book_Tag6 == 'Shojo' | 
                            Book_Tag7 == 'Shojo' |                      
                            Book_Tag8 == 'Shojo' |
                            Book_Tag9 == 'Shojo'~1,
                            TRUE ~ 0))
``` 

```{r making_a_Prostitution_dummy_variable}

book_domain <- book_domain %>%
  mutate( Prositution = case_when(Book_Tag1 == 'Prositution' | 
                                  Book_Tag2 == 'Prositution' | 
                                  Book_Tag3 == 'Prositution' |
                                  Book_Tag4 == 'Prositution' | 
                                  Book_Tag5 == 'Prositution' |
                                  Book_Tag6 == 'Prositution' |
                                  Book_Tag7 == 'Prositution' |                      
                                  Book_Tag8 == 'Prositution' |
                                  Book_Tag9 == 'Prositution'~1,
                                  TRUE ~ 0))
``` 

```{r making_a_Bande_Dessinee_dummy_variable}

book_domain <- book_domain %>%
  mutate( Bande_Dessinee = case_when(Book_Tag1 == 'BandeDessinee' | 
                                     Book_Tag2 == 'BandeDessinee' | 
                                     Book_Tag3 == 'BandeDessinee' |
                                     Book_Tag4 == 'BandeDessinee' | 
                                     Book_Tag5 == 'BandeDessinee' |
                                     Book_Tag6 == 'BandeDessinee' |
                                     Book_Tag7 == 'BandeDessinee' |                      
                                     Book_Tag8 == 'BandeDessinee' |
                                     Book_Tag9 == 'BandeDessinee'~1,
                                     TRUE ~ 0))
``` 

```{r making_a_Holocaust_dummy_variable}

book_domain <- book_domain %>%
  mutate( Holocaust = case_when(Book_Tag1 == 'Holocaust' | 
                                Book_Tag2 == 'Holocaust' | 
                                Book_Tag3 == 'Holocaust' |
                                Book_Tag4 == 'Holocaust' | 
                                Book_Tag5 == 'Holocaust' |
                                Book_Tag6 == 'Holocaust' |
                                Book_Tag7 == 'Holocaust' |                      
                                Book_Tag8 == 'Holocaust' |
                                Book_Tag9 == 'Holocaust'~1,
                                TRUE ~ 0))
``` 


```{r splitting_the_data}

set.seed(123)

domain_split <- initial_split(book_domain, 0.8)

domain_train <- training(domain_split)

domain_test <- testing(domain_split)

```

```{r}

log_reg5 <- glm(Challenged ~ LGBT + Mental_Health + New_Adult + Thriller +  Dystopia + Abuse +  Horror + Manga + African_American + Mental_Illness + Social_Justice + Witches + Race + War + Crime + Death + Religion + Politics + Sexuality + Africa + Autism + Cults + Dark + Disability + Jewish + Science + Seinen + Womens + Shojo + Prositution + Bande_Dessinee + Holocaust, data = domain_train, family = "binomial")

summary(log_reg5)
```

```{r}

log_reg6 <- glm(Challenged ~ LGBT + Mental_Health + New_Adult + Thriller + Mental_Illness, data = domain_train, family = "binomial")

summary(log_reg6)
```

The Model that I interpreted more was better, so I will use that one as my final model
